---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FinancialTool

<!-- badges: start -->
<!-- badges: end -->

The goal of **FinancialTool** is to simplify the analysis of financial data, specifically stock market data. It provides functions for calculating profits, analyzing stock performance, and more.

## Installation

You can install the development version of FinancialTool from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("OrlandoWillig/FinancialTool")
```

## Usage

**FinancialTool** is designed to be intuitive for those familiar with financial analysis in R. Here are a few basic examples:

### Calculating Portfolio Profits
Suppose you have a portfolio and stock data as follows:

```{r}
portfolio <- data.frame(
  Stock = c("StockA", "StockB"),
  Quantity = c(100, 50)
)
stock_data <- data.frame(
  Name = c("StockA", "StockB"),
  Last_Price = c(105, 210),
  Last_Price_Yesterday = c(100, 205)
)
```

You can calculate the profit (or loss) with:

```{r}
library(FinancialTool)
profits(portfolio, stock_data)
```


## Contributions
I welcome contributions, including bug reports, suggestions, and enhancements. Please open an issue or submit a pull request on our GitHub repository.